---
title: "LMPdata -- R package for the EU Labour Market Policy database"
output: github_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Installation

```{r, eval=FALSE}
# Either
install.packages('LMPdata') # once available on CRAN
# or
remotes::install_github('alekrutkowski/LMPdata')
```


# Explanations

The package provides an easy access to the "Labour Market Policy" statistics
database managed by the European Commission (Directorate-General for Employment,
Social Affairs & Inclusion). The data can be accessed also via
<https://webgate.ec.europa.eu/empl/redisstat/databrowser/explore/all/lmp?lang=en&display=card&sort=category>.


The package offers only two functions:

- `importData`
- `importLabels`

Usage examples:

```{r usage_examples}
library(LMPdata)

d <- importData(lmp_dataset_code = 'lmp_expsumm',
                filters = list(geo=c('AT','BE','CZ'), unit='MIO_EUR',
                               lmp_type='TOT1_9', exptype=c('XIND','XEMP')))
str(d)

g <- importLabels(dimension_code = "geo")
l <- importLabels(dimension_code = "exptype")
str(g)
str(l)
```

The following datasets are available:

|lmp_dataset_code|Description                                                                                           |
|----------------|------------------------------------------------------------------------------------------------------|
|LMP_EXPSUMM     |LMP expenditure by type of action -- summary tables                                                   |
|LMP_EXPME       |Detailed expenditure by LMP intervention                                                              |
|LMP_PARTSUMM    |LMP participants by type of action -- summary tables                                                  |
|LMP_PARTME      |Detailed data on participants by LMP intervention                                                     |
|LMP_IND_ACTSUP  |Activation-Support -- LMP participants per 100 persons wanting to work                                |
|LMP_IND_ACTRU   |Activation of registered unemployed                                                                   |
|LMP_IND_ACTIME  |Timely activation -- share of LMP entrants not previously long-term unemployed                        |
|LMP_IND_EXP     |LMP expenditure in convenient units (% of GDP or purchasing power standard per person wanting to work)|
|LMP_RJRU        |Persons registered with Public Employment Services                                                    |

The following dimensions are available:

|dimension_code|Description                                                                                           |
|--------------|------------------------------------------------------------------------------------------------------|
|AGE           |Age class                                                                                             |
|EXPTYPE       |Type of expenditure                                                                                   |
|GEO           |Geopolitical entity (reporting) i.e. a country                                                        |
|LMP_TYPE      |Labour market policy interventions by type of action                                                  |
|flags_        |Flags for each statistical observation                                                                |
|REGIS_ES      |Registration with employment services                                                                 |
|SEX           |Sex / gender                                                                                          |
|STK_FLOW      |Stock or flow                                                                                         |
|UNIT          |Unit of measure                                                                                       |
